The Linear Instability of Dilute Ultrarelativistic \epm\ Pair Beams

### 2016-07-01 oblique.tex
fixed numbering issue of Appendix and equation formatting

\documentclass[usenatbib,iop,apj]{emulateapj}
%\documentclass[usenatbib,iop,apj,numberedappendix]{aeb_emulateapj_2010}

@@

As stated in the Introduction, VHEGR photons pair produce on encountering EBL photons as they propagate throughout the universe \citep{Gould+66}, and this attenuation of VHEGR flux has been use as a probe of the EBL \citep{Stec-deJa-Sala:92,deJa-Stec-Sala:94,Ahar_etal:06}.
The basic requirement of this process is that the energies of the VHEGR ($E_{\rm ph}$) and the EBL photon
  ($E_{\rm ebl}$) exceed the rest mass energy of the $e^\pm$ pair in the center
  of momentum (COM) frame, i.e., $2 E E_{\rm ebl}(1-\cos\theta) \geq 4 m_e^2 c^4$, where
  $\theta$ is the relative angle of propagation in the lab frame, an $e^\pm$
  pair can be produced with Lorentz factor $\gamma\simeq E/2m_e c^2$
  \citep{Goul-Schr:67}.  Here, we discuss the distribution function of the pair beam that emerges from this process.

@@

In the COM frame of the beam, we assume that the distribution function is isotropic, such that $f=f(E)$ is just a function of energy.   This equilibrium energy distribution of a relativistic thermal plasma gas is
\begin{equation}\label{eq:relativistic maxwellian}
f\propto \exp\left(-\frac E T\right),
\end{equation}
 where $E$ and $T$ are the dimensionless energy and temperature in terms of a particles rest mass.  In the non-relativistic case, this reduces to the Maxwell-Boltzmann distribution, while the relativistic version is known as the Maxwell-Juttner distribution \citep{1911AnP...340..145J}.

The relativistic Maxwellian distribution can be extended to a drifting (or boosted) distribution via an appropriate Lorentz transformation.  The relationship between the energies of the lab (boosted) frame and the COM frame is
\begin{equation}
  E_{\rm CM} = \gamma_B\left(E_{\rm L} - \betaBOOST p_{\rm L,\parallel}\right).
\end{equation}
Plugging this into (\ref{eq:relativistic maxwellian}), we find the Maxwell-Juttner distribution \citep{1911AnP...340..145J,1975PhRvA..12..686W}
\begin{eqnarray}\label{eq:distribution function beam} %{eq:drifting maxwellian}
%f = \frac{1}{4\pi\gamma_B m^2 T_{\rm L} K_2(m/T_{\rm L})} \exp\left(-\frac {E_{\rm L} - \betaBOOST p_{\rm L,\parallel}} {T_{\rm L}}\right), \\
f = \frac{n_b m_e c^2}{4\pi\gamma_B k_B T K_2(m_ec^2/k_B T )m_e^3c^3} \exp\left(-\frac {\gamma_B(E - \vel_B\cdot \bmath{p})} {k_B T}\right)
\end{eqnarray}
where $K_2$ is the 2nd order modified Bessel function.

%The transformation properties of the drifting Maxwell-Juttner distribution coupled with the Lorentz invariance of the distribution function (as discussed in Appendix~\ref{sec:lorentz}) demonstrates that the drifting Maxwell-Juttner distribution is the correct description of a boosted isotropic Maxwellian (relativistic or otherwise).

@@

% To see how this distribution function appears in velocity space, we show four examples of the  Maxwell-Juttner distribution in the center-of-mass frame for the nonrelativistic temperatures ($T=10^{-2}$ and $ 0.1$) in Figure \ref{fig:distribution_non_rel} and for relativistic temperatures ( $T=1$ and $10$) in Figure \ref{fig:distribution_rel}, where $T$ is listed in the natural relativistic units: $m_e c^2/k_B$.

@@

We begin first with the distribution function for the target plasma:
\begin{equation}
 F_t = \left(\frac{1}{2\pi m_e k_B T}\right)^{3/2}\exp\left(-\frac{p^2}{2m_e k_B T}\right),
\end{equation}
where the target plasma is assumed to be nonrelativistic, $\bmath{p}=m_e\vel$ is the nonrelativistic momentum,  and$T$ is the temperature of the background.
For the beam plasma, we adopt the Maxwell-Juttner distribution (eq.[\ref{eq:distribution function beam}]).
%\begin{equation}\label{eq:distribution function beam}
%F_b = \frac{n_b}{4\pi\gamma_B m^2 T K_2(m/T_{\rm L})} \exp\left(-\frac {\gammabeam(E - \betabeam \cdot \pmom)} {T}\right),
%\end{equation}
Plugging these into the dispersion relation (\ref{eq:dispersion relation}), we find
%\begin{equation}\label{eq:dispersion kinetic}
% 1 - \frac{\omega_{p,t}^2}{k}\int F_t\frac{k^2 - (\kvec\cdot\betavec)^2}{\gamma(\omega - \kvec\cdot\vel)^2} d^3p - \frac{\omega_{p,t}^2}{k}\int \frac{\kvec\cdot\gradp F_b}{\omega - \kvec\cdot\vel}d^3p  = 0,
%\end{equation}
\begin{equation}\label{eq:dispersion kinetic}
 1 - \frac{\omega_{p,t}^2}{k^2c^2}\int F_t\frac{k^2c^2 - (\kvec\cdot\vel)^2}{\gamma(\omega - \kvec\cdot\vel)^2} d^3p + \frac{m_e\omega_{p,b}^2}{k^2}\int \frac{\kvec\cdot\gradp F_b}{\omega - \kvec\cdot\vel}d^3p  = 0,
\end{equation}
where we have integrated by parts only the second term, associated with target plasma.

We discuss the solution to Equation (\ref{eq:dispersion kinetic}) in Appendix \ref{sec:solution kinetic}.  The associate growth rate for the kinetic beam plasma instability is  
\begin{equation}
\Gamma \simeq - \Gamma_0
\frac{\pi \gamma_w^2 \gph^3 m (\vph-v_{B,z'})}{4 \gamma_b \mu K_2(\mu) \cG'^3}
\left[
\left( \cG'^2\mu^2 + 2\cG'\mu + 2 \right) 
+
\frac{\gamma_B^2 v_{B,x'}^2}{2\cG^2c^2} \left(2 \cG'\mu+ 2\right)
\right]
\exp(-\cG'\mu),\label{eq:kinetic growth rate}
\end{equation}
where $\Gamma_0 \equiv \omega_p \gamma_B (n_b/n_t) (m_e v_B^2/k_B T)$ is the typical maximum growth rate.  This specializes to the beam-plasma growth rate if we take $v_{B,x'} = 0$, which gives:
\begin{equation}
\Gamma_{\rm bp} \simeq - \Gamma_0
\frac{\pi \gamma_w^2 \gph^3 m (\vph-v_{B,z'})}{4 \gamma_b \mu K_2(\mu) \cG'^3}
\left( \cG'^2\mu^2 + 2\cG'\mu + 2 \right) 
\exp(-\cG'\mu),\label{eq:bp kinetic growth rate}
\end{equation}

@@

Still some progress can be made if we assume that the dominant loss rate is ICC so that we can place a lower limit on the various plasma processes.  In this case, the ratio of the beam plasma density to the IGM, $n_b/\nIGM$, is then (Paper I):
\begin{eqnarray}
\frac{\nb}{\nIGM} &\simeq&
\frac{L_E}{2\pi\Dpp^3\GIC}\frac{1}{\nIGM} \nonumber\\
&\simeq &
3\times10^{-18}
\left(\frac{1+z}{1}\right)^{3\zeta-7}
\left(\frac{E L_E}{10^{45}\erg\,\s^{-1}}\right)
\left(\frac{E}{\TeV}\right)
\,\cm^{-3}\,,
\label{eq:nbIC}
\end{eqnarray}
where $\Dpp$ is defined in the Introduction to be the mean free path of a VHEGR, $L_E$ is the isotropic luminosity of the VHEGR source, $E$ is the energy of the VHEGR photon, $\Gamma_{\rm IC}$ is the inverse Compton cooling rate, and $\zeta = 4.5$ for $z \leq 1$ and $\zeta = 0$ for $z\geq 1$.

In Section \ref{sec:transition}, we derived the controlling parameter that delineates the reactive (eq.[\ref{eq:generic reactive regime}]) and kinetic regimes (eq.[\ref{eq:generic kinetic regime}]) by comparing the frequency spread of resonant waves, $\Delta\omega\sim k\Delta v$, with the growth rate, $\Gamma$.  Applying these conditions (eqns. [\ref{eq:generic reactive regime}] and [\ref{eq:generic kinetic regime}]) to the ultrarelativistic $e^+e^-$ pair beams of interest, we find for the controlling parameter: 
\begin{eqnarray}
\frac{\gamma_b^{2/3}}{\sqrt{k_BT/m_e c^2}}\left(\frac{n_b}{\nIGM}\right)^{1/3} &=& 3.2\times 10^{-2} \frac{\gamma_6^{2/3}}{\sqrt{k_BT/m_e c^2}}\left(\frac{1+z}{2}\right)^{\zeta-7/3}\nonumber\\
&&\left(\frac{E L_E}{10^{45}\erg\,\s^{-1}}\right)^{1/3}
\left(\frac{E}{\TeV}\right)^{1/3},\label{eq:beam oblique condition}
\end{eqnarray}
and
\begin{eqnarray}
\frac{\gamma_b}{\sqrt{k_BT/m_e c^2}}\left(\frac{n_b}{\nIGM}\right)^{1/3} &=& 3.2 \frac{\gamma_6}{\sqrt{k_BT/m_e c^2}}\left(\frac{1+z}{2}\right)^{\zeta-7/3}\nonumber\\
&&\left(\frac{E L_E}{10^{45}\erg\,\s^{-1}}\right)^{1/3}
\left(\frac{E}{\TeV}\right)^{1/3},\label{eq:beam bp condition}
\end{eqnarray}
where $\gamma_6 = \gamma/10^6$. 
We see from our reactive (\ref{eq:generic reactive regime}) and kinetic (\ref{eq:generic kinetic regime}) conditions, that the oblique instability always exists in the kinetic regime, but the beam plasma instability sits in the reactive regime at $z\gtrsim 1$ or for sufficiently cold beams $k_BT/m_e c^2 \lesssim 0.5$, which occurs $E_{\rm ph} \sim 1\,\TeV$ and for large $\gamma$, which occurs for $E_{\rm ph} \sim 10\,\TeV$ at $z=0$.

@@

The ultrarelativistic $\epm$ beams that result from VHEGR-EBL annihilation are subject to powerful plasma beam instabilities including the beam plasma and oblique instability.  In this work, we have these linear instabilities as they would apply to the ultrarelativistic pair beams.  Our main findings are:
\begin{itemize}
%\item{We calculate how the parallel and perpendicular velocity dispersions of a distribution function responds under Lorentz boosts.  We show that these two velocities dispersions respectively scale like $\gamma^{-2}$ and $\gamma^{-1}$, allowing us to develop a simplified distribution function of the TeV electron-positron beam. We also show that this can be identified with a drifting relativistic Maxwell-Juttner distribution. }
\item{We analytically calculated the beam-plasma and oblique instabilities in both the reactive and kinetic regime.  We have recovered the reactive scalings for the beam-plasma mode $\Gamma \sim \gamma^{-1}(n_b/n_t)^{1/3}$ and the oblique mode $\Gamma \sim (n_b/\gamma n_t)^{1/3}$.  In the kinetic regime, we have shown that the growth rate for both modes have the same scaling and similar normalization.}
\item{We also delineated the regime of applicability of the kinetic and reactive calculation and found, while the kinetic growth rates are similar for both the beam plasma and oblique mode, the condition for transition between the kinetic and reactive regimes for both are different.  In particular, the beam-plasma mode transitions at a lower value of $\gamma$ in comparison to the oblique mode.  This is due to a difference of $\gamma^{1/3}$ scaling between the two modes.}
\item{We calculate the average COM energy of the ultrarelativistic pair beam using a simplified model of the spectra of the EBL.  We found that the average energy of these beams range from $E_e/m_e c^2 = 1.3-3$ for $E_{\rm ph} = 1-10\,\TeV$, with colder beams at lower energies.  This is due to the rapid cutoff in the EBL above $10\,\eV$. }
\item{We demonstrate that the oblique mode is in the kinetic regime, while, the beam plasma mode is marginally in the reactive regime. In any case, the use of either regime produces roughly the same growth rate.  Moreover, the inclusion of plasma instability losses on the number density of beam particles may place the beam plasma mode firmly in the kinetic regime.}
\end{itemize}

@@

%\onecolappendix
\appendix%[onecolumn]
%\onecolumn

@@

>>>>

%\documentclass[usenatbib,iop,apj]{emulateapj}
\documentclass[usenatbib,iop,apj,numberedappendix]{aeb_emulateapj_2015}

@@

As stated in the Introduction, VHEGR photons pair produce on encountering EBL
photons as they propagate throughout the universe \citep{Gould+66}, and this
attenuation of VHEGR flux has been used as a probe of the EBL
\citep{Stec-deJa-Sala:92,deJa-Stec-Sala:94,Ahar_etal:06}.  The basic requirement
of this process is that the energies of the VHEGR ($E_{\rm ph}$) and the EBL
photon ($E_{\rm ebl}$) exceed the rest mass energy of the $e^\pm$ pair in the
center of momentum (COM) frame, i.e., $2 E E_{\rm ebl}(1-\cos\theta) \geq 4
m_e^2 c^4$, where $\theta$ is the relative angle of propagation in the lab
frame\cp{\sout{,}. As a result,} an $e^\pm$ pair can be produced with Lorentz factor $\gamma\simeq E/2m_e
c^2$ \citep{Goul-Schr:67}.  Here, we discuss the distribution function of the
pair beam that emerges from this process.

@@

In the COM frame of the beam, we assume that the distribution function is isotropic, such that $f=f(E)$ is just a function of energy.   This equilibrium energy distribution of a relativistic thermal plasma gas is
\begin{equation}\label{eq:relativistic maxwellian}
f\propto \exp\left(-\frac E T\right),
\end{equation}
 where $E$ and $T$ are the dimensionless energy and temperature in terms of a particles rest mass.  In the non-relativistic case, this reduces to the Maxwell-Boltzmann distribution, while the relativistic version is known as the Maxwell-J{\"u}ttner distribution \citep{1911AnP...340..145J}.

The relativistic Maxwellian distribution can be extended to a drifting (or boosted) distribution via an appropriate Lorentz transformation.  The relationship between the energies of the lab (boosted) frame and the COM frame is
\begin{equation}
  E_{\rm CM} = \gamma_B\left(E_{\rm L} - \betaBOOST p_{\rm L,\parallel}\right).
\end{equation}
\cp{\sout{Plugging}Inserting} this into (\ref{eq:relativistic maxwellian}), we find the Maxwell-J{\"u}ttner distribution \citep{1911AnP...340..145J,1975PhRvA..12..686W}
\begin{eqnarray}\label{eq:distribution function beam} %{eq:drifting maxwellian}
%f = \frac{1}{4\pi\gamma_B m^2 T_{\rm L} K_2(m/T_{\rm L})} \exp\left(-\frac {E_{\rm L} - \betaBOOST p_{\rm L,\parallel}} {T_{\rm L}}\right), \\
f = \frac{n_b m_e c^2}{4\pi\gamma_B k_B T K_2(m_ec^2/k_B T )m_e^3c^3} \exp\left(-\frac {\gamma_B(E - \vel_B\cdot \bmath{p})} {k_B T}\right)
\end{eqnarray}
where $K_2$ is the 2nd order modified Bessel function.

%The transformation properties of the drifting Maxwell-J{\"u}ttner distribution coupled with the Lorentz invariance of the distribution function (as discussed in Appendix~\ref{sec:lorentz}) demonstrates that the drifting Maxwell-J{\"u}ttner distribution is the correct description of a boosted isotropic Maxwellian (relativistic or otherwise).

@@

% To see how this distribution function appears in velocity space, we show four examples of the  Maxwell-J{\"u}ttner distribution in the center-of-mass frame for the nonrelativistic temperatures ($T=10^{-2}$ and $ 0.1$) in Figure \ref{fig:distribution_non_rel} and for relativistic temperatures ( $T=1$ and $10$) in Figure \ref{fig:distribution_rel}, where $T$ is listed in the natural relativistic units: $m_e c^2/k_B$.

@@

We begin first with the distribution function for the target plasma:
\begin{equation}
 F_t = \left(\frac{1}{2\pi m_e k_B T}\right)^{3/2}\exp\left(-\frac{p^2}{2m_e k_B T}\right),
\end{equation}
where the target plasma is assumed to be nonrelativistic, $\bmath{p}=m_e\vel$ is the nonrelativistic momentum,  and$T$ is the temperature of the background.
For the beam plasma, we adopt the Maxwell-J{\"u}ttner distribution (eq.[\ref{eq:distribution function beam}]).
%\begin{equation}\label{eq:distribution function beam}
%F_b = \frac{n_b}{4\pi\gamma_B m^2 T K_2(m/T_{\rm L})} \exp\left(-\frac {\gammabeam(E - \betabeam \cdot \pmom)} {T}\right),
%\end{equation}
Plugging these into the dispersion relation (\ref{eq:dispersion relation}), we find
%\begin{equation}\label{eq:dispersion kinetic}
% 1 - \frac{\omega_{p,t}^2}{k}\int F_t\frac{k^2 - (\kvec\cdot\betavec)^2}{\gamma(\omega - \kvec\cdot\vel)^2} d^3p - \frac{\omega_{p,t}^2}{k}\int \frac{\kvec\cdot\gradp F_b}{\omega - \kvec\cdot\vel}d^3p  = 0,
%\end{equation}
\begin{equation}\label{eq:dispersion kinetic}
 1 - \frac{\omega_{p,t}^2}{k^2c^2}\int F_t\frac{k^2c^2 - (\kvec\cdot\vel)^2}{\gamma(\omega - \kvec\cdot\vel)^2} d^3p + \frac{m_e\omega_{p,b}^2}{k^2}\int \frac{\kvec\cdot\gradp F_b}{\omega - \kvec\cdot\vel}d^3p  = 0,
\end{equation}
where we have integrated by parts only the second term, associated with target plasma.

We discuss the solution to Equation (\ref{eq:dispersion kinetic}) in Appendix \ref{sec:solution kinetic}.  The associate growth rate for the kinetic beam plasma instability is  
\begin{equation}
\begin{aligned}
\Gamma &\simeq - \Gamma_0
\frac{\pi \gamma_w^2 \gph^3 m (\vph-v_{B,z'})}{4 \gamma_b \mu K_2(\mu) \cG'^3}\\
&\times\left[
\left( \cG'^2\mu^2 + 2\cG'\mu + 2 \right) 
+
\frac{\gamma_B^2 v_{B,x'}^2}{2\cG^2c^2} \left(2 \cG'\mu+ 2\right)
\right]
\exp(-\cG'\mu),\label{eq:kinetic growth rate}
\end{aligned}
\end{equation}
where $\Gamma_0 \equiv \omega_p \gamma_B (n_b/n_t) (m_e v_B^2/k_B T)$ is the typical maximum growth rate.  This specializes to the beam-plasma growth rate if we take $v_{B,x'} = 0$, which gives:
\begin{equation}
\Gamma_{\rm bp} \simeq - \Gamma_0
\frac{\pi \gamma_w^2 \gph^3 m (\vph-v_{B,z'})}{4 \gamma_b \mu K_2(\mu) \cG'^3}
\left( \cG'^2\mu^2 + 2\cG'\mu + 2 \right) 
\exp(-\cG'\mu),\label{eq:bp kinetic growth rate}
\end{equation}

@@

Still some progress can be made if we assume that the dominant loss rate is ICC so that we can place a lower limit on the various plasma processes.  In this case, the ratio of the beam plasma density to the IGM, $n_b/\nIGM$, is then (Paper I):
\begin{eqnarray}
\frac{\nb}{\nIGM} &\simeq&
\frac{L_E}{2\pi\Dpp^3\GIC}\frac{1}{\nIGM} \\
&\simeq &
3\times10^{-18}
\left(\frac{1+z}{1}\right)^{3\zeta-7}
\left(\frac{E L_E}{10^{45}\erg\,\s^{-1}}\right)
\left(\frac{E}{\TeV}\right)
\,\cm^{-3}\,,\nonumber
\label{eq:nbIC}
\end{eqnarray}
where $\Dpp$ is defined in the Introduction to be the mean free path of a VHEGR, $L_E$ is the isotropic luminosity of the VHEGR source, $E$ is the energy of the VHEGR photon, $\Gamma_{\rm IC}$ is the inverse Compton cooling rate, and $\zeta = 4.5$ for $z \leq 1$ and $\zeta = 0$ for $z\geq 1$.

In Section \ref{sec:transition}, we derived the controlling parameter that delineates the reactive (eq.[\ref{eq:generic reactive regime}]) and kinetic regimes (eq.[\ref{eq:generic kinetic regime}]) by comparing the frequency spread of resonant waves, $\Delta\omega\sim k\Delta v$, with the growth rate, $\Gamma$.  Applying these conditions (eqns. [\ref{eq:generic reactive regime}] and [\ref{eq:generic kinetic regime}]) to the ultrarelativistic $e^+e^-$ pair beams of interest, we find for the controlling parameter: 
\begin{eqnarray}
\frac{\gamma_b^{2/3}}{\sqrt{k_BT/m_e c^2}}\left(\frac{n_b}{\nIGM}\right)^{1/3} &=& 3.2\times 10^{-2} \frac{\gamma_6^{2/3}}{\sqrt{k_BT/m_e c^2}}\left(\frac{1+z}{2}\right)^{\zeta-7/3}\nonumber\\
&&\left(\frac{E L_E}{10^{45}\erg\,\s^{-1}}\right)^{1/3}
\left(\frac{E}{\TeV}\right)^{1/3},\label{eq:beam oblique condition}
\end{eqnarray}
and
\begin{eqnarray}
\frac{\gamma_b}{\sqrt{k_BT/m_e c^2}}\left(\frac{n_b}{\nIGM}\right)^{1/3} &=& 3.2 \frac{\gamma_6}{\sqrt{k_BT/m_e c^2}}\left(\frac{1+z}{2}\right)^{\zeta-7/3}\nonumber\\
&&\left(\frac{E L_E}{10^{45}\erg\,\s^{-1}}\right)^{1/3}
\left(\frac{E}{\TeV}\right)^{1/3}\label{eq:beam bp condition}
\end{eqnarray}
where $\gamma_6 = \gamma/10^6$. 
We see from our reactive (\ref{eq:generic reactive regime}) and kinetic (\ref{eq:generic kinetic regime}) conditions, that the oblique instability always exists in the kinetic regime, but the beam plasma instability sits in the reactive regime at $z\gtrsim 1$ or for sufficiently cold beams $k_BT/m_e c^2 \lesssim 0.5$, which occurs $E_{\rm ph} \sim 1\,\TeV$ and for large $\gamma$, which occurs for $E_{\rm ph} \sim 10\,\TeV$ at $z=0$.

@@

The ultrarelativistic $\epm$ beams that result from VHEGR-EBL annihilation are subject to powerful plasma beam instabilities including the beam plasma and oblique instability.  In this work, we have these linear instabilities as they would apply to the ultrarelativistic pair beams.  Our main findings are:
\begin{itemize}
%\item{We calculate how the parallel and perpendicular velocity dispersions of a distribution function responds under Lorentz boosts.  We show that these two velocities dispersions respectively scale like $\gamma^{-2}$ and $\gamma^{-1}$, allowing us to develop a simplified distribution function of the TeV electron-positron beam. We also show that this can be identified with a drifting relativistic Maxwell-J{\"u}ttner distribution. }
\item{We analytically calculated the beam-plasma and oblique instabilities in both the reactive and kinetic regime.  We have recovered the reactive scalings for the beam-plasma mode $\Gamma \sim \gamma^{-1}(n_b/n_t)^{1/3}$ and the oblique mode $\Gamma \sim (n_b/\gamma n_t)^{1/3}$.  In the kinetic regime, we have shown that the growth rate for both modes have the same scaling and similar normalization.}
\item{We also delineated the regime of applicability of the kinetic and reactive calculation and found, while the kinetic growth rates are similar for both the beam plasma and oblique mode, the condition for transition between the kinetic and reactive regimes for both are different.  In particular, the beam-plasma mode transitions at a lower value of $\gamma$ in comparison to the oblique mode.  This is due to a difference of $\gamma^{1/3}$ scaling between the two modes.}
\item{We calculate the average COM energy of the ultrarelativistic pair beam using a simplified model of the spectra of the EBL.  We found that the average energy of these beams range from $E_e/m_e c^2 = 1.3-3$ for $E_{\rm ph} = 1-10\,\TeV$, with colder beams at lower energies.  This is due to the rapid cutoff in the EBL above $10\,\eV$. }
\item{We demonstrate that the oblique mode is in the kinetic regime, while, the beam plasma mode is marginally in the reactive regime. In any case, the use of either regime produces roughly the same growth rate.  Moreover, the inclusion of plasma instability losses on the number density of beam particles may place the beam plasma mode firmly in the kinetic regime.}
\end{itemize}

@@

%\onecolappendix
%\appendix%[onecolumn]
%\onecolumn
\begin{appendix}

@@

\end{appendix}
